Certified Knowledge Compilation \\ with Application to Verified Model Counting \\ Experimental Details

### 2023-08-29 doc/JAIR/jair-data.tex
Tweaks

We tried various experiments where the proof generator starts at the
top using a structural approach and then switches to a monolithic
approach once the tree size for a node drops below some threshold.  We
could not find any selection procedure that improved the overall
performance for the 90 smaller benchmarks.  On the other hand, it
proved useful for the very large benchmarks, because calling a SAT
solver on a problem with more than $10^6$ clauses often causes the
solver to fail.  We therefore refined the rule into a \emph{hybrid} approach to operate as follows:
\begin{enumerate}
\item Label all nodes by the tree size of the subgraph for which it is the root.
\item Compute the total size of the graph and the tree ratio of the root.
\item Proceed with proof generation with the following rules
  \begin{enumerate}
  \item If the tree ratio is below 5.0 and the tree size of the root is below $10^6$, do the entire proof generation with a monolithic approach
  \item If the tree ratio is below 5.0 and the tree size of the root is above $10^6$, start with a structural approach and shift to a monolithic approach once the tree size at a node is below $10^6$.
  \item If the tree ratio is above 5.0, do the entire proof generation
    with a structural approach.
  \end{enumerate}
\end{enumerate}

>>>>

We tried various experiments where the proof generator starts at the
top using a structural approach and then switches to a monolithic
approach once the tree size for a node drops below some threshold.
This was helpful for very large benchmarks, using high thresholds.
We also found that SAT solvers could not reliably handle problems with $10^7$ or more clauses.
We therefore refined the rule into a \emph{hybrid} approach that operates as follows:
\begin{enumerate}
\item With a bottom-up traversal of the graph, Label each node by the tree size of the subgraph for which it is the root.
\item Compute the total size of the graph and the tree ratio of the root.
\item Proceed with proof generation with the following rules
  \begin{enumerate}
  \item If the tree ratio is below 5.0 and the tree size of the root is below $10^6$, do the entire proof generation with a monolithic approach
  \item If the tree ratio is below 5.0 and the tree size of the root is above $10^6$, start with a structural approach and shift to a monolithic approach once the tree size at a node is below $10^6$.
  \item If the tree ratio is above 5.0, do the entire proof generation
    with a structural approach.
  \end{enumerate}
\end{enumerate}
Unless noted otherwise, The remainder of our experimental data is based on this approach.
